### 2025-11-14 sports-cognitive-psychology.qmd
20250910 - artificial intelligence
20251114 - typo

Nevertheless, more and more people around the league use analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) [@Clark2018; archived at <https://perma.cc/7BKP-A4GJ>] and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) [@Awbrey2020; archived at <https://perma.cc/WXE3-53E6>].
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) [@Fox2021; archived at <https://perma.cc/49KQ-R785>] and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) [@Rosenthal2018; archived at <https://perma.cc/2GRF-8Z5K>].

@@

As depicted in the @fig-goForItPercentageByWinProbChange [which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); @R-nfl4th; archived at <https://perma.cc/S5D8-3NCU>], teams went for it on fourth down nearly twice as often in 2021 compared to 2017, when when their win probability was at least 20% (given the current situation at the start of the given play) and they would increase their win probably by going for it.
We use the `ggtext` package [@R-ggtext] to annotate text:

>>>>

Nevertheless, more and more people around the league use analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) [@Clark2018; archived at <https://perma.cc/7BKP-A4GJ>] and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) [@Awbrey2020; archived at <https://perma.cc/WXE3-53E6>].
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) [@Fox2021; archived at <https://perma.cc/49KQ-R785>] and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) [@Rosenthal2018; archived at <https://perma.cc/2GRF-8Z5K>].
Moreover, teams are now using artificial intelligence (AI) to help them prepare for games, evaluate players, make draft selections, and perform game management [@Levi2025; archived at <https://perma.cc/XF2Z-ZZZT>].

@@

As depicted in the @fig-goForItPercentageByWinProbChange [which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); @R-nfl4th; archived at <https://perma.cc/S5D8-3NCU>], teams went for it on fourth down nearly twice as often in 2021 compared to 2017, when their win probability was at least 20% (given the current situation at the start of the given play) and they would increase their win probability by going for it.
We use the `ggtext` package [@R-ggtext] to annotate text:
